---
title: "American option pricing"
author: "Yu DAI"
date: "7/9/2019"
output: html_document
---

```{r}
rand2<-function(numran,idum=-1){  
  IM1=2147483563
  IM2=2147483399
  IMM1=IM1-1
  IA1=40014
  IA2=40692
  IQ1=53668
  IQ2=52774
  IR1=12211
  IR2=3791
  NTAB=32
  NDIV=1+IMM1/NTAB
  #make sure that you initializa the generator with a non-positive idum. 
  if(idum>0){idum=-idum}
  
  idum2=123456789
  iv=rep(0,NTAB)
  iy=0
  #real number
  AM=1./IM1
  EPS=1.2e-7
  RNMX=1.-EPS#number very close to 1
  random<-rep(0,numran)
  icount=1
  for(icount in 1:numran){
    if(idum<=0){
      idum<-max(-idum,1)
      idum2=idum
      j=NTAB+8
      while(j>0){
        k<-as.integer(idum/IQ1)
        idum<-IA1*(idum-k*IQ1)-k*IR1
        if(idum<0){
          idum<-idum+IM1
        }
        if(j<33){iv[j]<-idum}
        j<-j-1
      }
      iy<-iv[1]
    }
    k<-as.integer(idum/IQ1)
    idum<-IA1*(idum-k*IQ1)-k*IR1
    if(idum<0){idum<-idum+IM1}
    k<-as.integer(idum2/IQ2)
    idum2=IA2*(idum2-k*IQ2)-k*IR2
    if(idum2<0){idum2<-idum2+IM2}
    j<-1+as.integer(iy/NDIV)
    iy<-iv[j]-idum2
    iv[j]<-idum
    if(iy<1){iy<-iy+IMM1}
    ran2<-min(AM*iy,RNMX)
    random[icount]<-ran2
  }
  return(random)
}

gassMap<-function(idum){
  #input: idum between 0 and 1
  #output: x,approximation to inverse normal cdf
  a0=2.50662823884
  a1=-18.61500062529
  a2=41.39119773534
  a3=-25.44106049637
  b0=-8.47351093090
  b1=23.08336743743
  b2=-21.06224101826
  b3=3.13082909833
  C<-c(0.3374754822726147,0.9761690190917186,0.1607979714918209
       ,0.0276438810333863,0.0038405729373609,0.0003951896511919
       ,0.0000321767881768,0.0000002888167364,0.0000003960315187)
  
  y<-idum-0.5
  if(abs(y)<0.42){
    r<-y*y
    x<-y*(((a3*r+a2)*r+a1)*r+a0)/((((b3*r+b2)*r+b1)*r+b0)*r+1)
  }
  else{
    r<-idum
    if(y>0){r<-1-idum}
    r<-log(-log(r))
    x<-C[1]+r*(C[2]+r*(C[3]+r*(C[4]+r*(C[5]+r*(C[6]+r*(C[7]+r*(C[8]+r*C[9])))))))
    if(y<0){x<-(-x)}
  }
  return(x)
}
#this is a function that generate normal distributed random number 
gassrand<-function(numran,idum=-1){
  if(idum>0){idum=-idum}
  randnum=rand2(numran,idum)
  gassRand=rep(0,length(randnum))
  for(i in 1:length(randnum)){
    gassRand[i]<-gassMap(randnum[i])
  }
  return(gassRand)
}
```
Function that will simulate stock price given S0,drift,vol,r
```{r}
MY_Stock_Simu<-function(num_grid,path_num,dt,drift,vol,S0){
  randomwalk<-gassrand(num_grid*path_num,0)
  randomwalk<-t(matrix(data=randomwalk,nrow = num_grid, ncol = path_num,byrow = FALSE,dimnames = NULL))
  price_path<-matrix(data = 0, nrow = path_num, ncol = num_grid+1, byrow = FALSE,dimnames = NULL)
  price_path[,1]<-rep(S0,path_num)
  #simulate stock path
  for(i in 1:path_num){
    for(j in 1:num_grid){
      price_path[i,j+1]=price_path[i,j]*exp((drift*dt+vol*sqrt(dt)*randomwalk[i,j])) 
    }
  }
  return(price_path)
}
```

Thus by hedging with the option, bank can reduce its risk.
```{r}
dt=2/52 #bi_weely grid
K=100
t=0.5
S0=100
vol=0.25
r=0.03
m<-13
n<-10000
drift<-r-0.5*vol*vol
Simu_stock<-MY_Stock_Simu(m,n,dt,drift,vol,S0)
```
(2) Evaluation for early exercise is every two weeks, I define a function to calculated American option price based on barrier that user gives
```{r }
Us_option<-function(n,m,barrier,stocke_price,K){
  option_value<-rep(0,n)
  dt<-2/52
  t_t_T<-m*dt
  r<-0.03
  t_n<-m #value every 2 weekd
  for(i in 1:n){
    for(j in 2:t_n){
     if(Simu_stock[i,j]<=barrier){
        #early exercise
        option_value[i]=(K-stocke_price[i,j])*exp(-(j)*dt*r)
        break;
      }
      option_value[i]=max((K-stocke_price[i,j]),0)*exp(-t_t_T*r)
      
    }
  }
  return( mean(option_value))
}

```
(3) Determine the level of the barrier that maximized the value of the put option
To make my code more effient:
First,I use a series a grid of 1 from K/50 to K and calculated the option price for each barrier
Second, I find the grid that has the maxinum price,best_grid1
Third, I set a a series a grid of 0.1 from (best_grid1-1) to (best_grid1+1)
Then, I find the grid that has the maxinum price,best_grid2
Then, I set a a series a grid of 0.01 from (best_grid1-1) to (best_grid1+1)
#By doing this,I can find the target grid doing the calculation for 80*n*m of precision of 0.001,  vs doing 50000*n*m  times
```{r }
barrier<-seq(50, 100, 1 )
l<-length(barrier)
option_price<-rep(0,l)
for(i in 1:l){
  option_price[i]<-Us_option(n,m,barrier[i],Simu_stock,K)
}

for(i in 1:3){
I1=which.max(option_price)
low=I1-1
up=I1+1
barrier<-seq(barrier[low], barrier[up], 1/10**i )
l<-length(barrier)
option_price<-rep(0,l)
for(j in 1:l){
  option_price[j]<-Us_option(n,m,barrier[j],Simu_stock,K)
}
}
I1=which.max(option_price)
optimized_barrier<-barrier[I1]
optimized_option_price<-option_price[I1]

cat('optimized barrier is: ',optimized_barrier)
cat('\nEuropean option price is: ',Us_option(n,m,0,Simu_stock,K))
cat('\noptimized American option price is',optimized_option_price)
#given a barrier that stock price cannot reach==>Np early exercise==>european option price
```

As we can see that our American option price > European option price for the same parameters,which is consistent with the reality that American option is expensive than European option.

## Check the value of the American put against the value determined by a Binomial Model
```{r }
# Binomial Model
numsteps<-13
DelT <- 2/52 
uptick<-exp(+vol*sqrt(DelT))
dntick<-exp(-vol*sqrt(DelT))
FVFactor<-exp(r*DelT)
probup<-(FVFactor-dntick)/(uptick-dntick)
probdn<-1-probup
SMat<-matrix(rep(0),nrow=numsteps,ncol=numsteps)
EMat<-matrix(rep(0),nrow=numsteps,ncol=numsteps)
AMat<-matrix(rep(0),nrow=numsteps,ncol=numsteps)
for (i in 1:numsteps) {
  for (j in 1:i) {
    SMat[j,i]<-S0*uptick^(i-j)*dntick^(j-1) 
}}

i<-numsteps
for (j in 1:i) {
  EMat[j,numsteps]<-max(K-SMat[j,numsteps],0)
  AMat[j,numsteps]<-max(K-SMat[j,numsteps],0)
}
i<-i-1
while (i > 0) {
  for (j in 1:i) {
    EMat[j,i] <- (1/FVFactor)*(probup*EMat[j,i+1] + probdn*EMat[j+1,i+1])
    AMat[j,i] <- (1/FVFactor)*(probup*AMat[j,i+1] + probdn*AMat[j+1,i+1])
    AMat[j,i] <- max(AMat[j,i],K-SMat[j,i])
    }
    i<-i-1
}

cat('European option price is: ',EMat[1,1],'\n')
cat('American option price is: ',AMat[1,1],'\n')
```
