---
title: "Simulation HW#4 Q1"
author: "Yu DAI"
date: "2019/5/6"
output: html_document
---

```{r}
rand2<-function(numran,idum=-1){  
  IM1=2147483563
  IM2=2147483399
  IMM1=IM1-1
  IA1=40014
  IA2=40692
  IQ1=53668
  IQ2=52774
  IR1=12211
  IR2=3791
  NTAB=32
  NDIV=1+IMM1/NTAB
  #make sure that you initializa the generator with a non-positive idum. 
  if(idum>0){idum=-idum}
  
  idum2=123456789
  iv=rep(0,NTAB)
  iy=0
  #real number
  AM=1./IM1
  EPS=1.2e-7
  RNMX=1.-EPS#number very close to 1
  random<-rep(0,numran)
  icount=1
  for(icount in 1:numran){
    if(idum<=0){
      idum<-max(-idum,1)
      idum2=idum
      j=NTAB+8
      while(j>0){
        k<-as.integer(idum/IQ1)
        idum<-IA1*(idum-k*IQ1)-k*IR1
        if(idum<0){
          idum<-idum+IM1
        }
        if(j<33){iv[j]<-idum}
        j<-j-1
      }
      iy<-iv[1]
    }
    k<-as.integer(idum/IQ1)
    idum<-IA1*(idum-k*IQ1)-k*IR1
    if(idum<0){idum<-idum+IM1}
    k<-as.integer(idum2/IQ2)
    idum2=IA2*(idum2-k*IQ2)-k*IR2
    if(idum2<0){idum2<-idum2+IM2}
    j<-1+as.integer(iy/NDIV)
    iy<-iv[j]-idum2
    iv[j]<-idum
    if(iy<1){iy<-iy+IMM1}
    ran2<-min(AM*iy,RNMX)
    random[icount]<-ran2
  }
  return(random)
}

gassMap<-function(idum){
  #input: idum between 0 and 1
  #output: x,approximation to inverse normal cdf
  a0=2.50662823884
  a1=-18.61500062529
  a2=41.39119773534
  a3=-25.44106049637
  b0=-8.47351093090
  b1=23.08336743743
  b2=-21.06224101826
  b3=3.13082909833
  C<-c(0.3374754822726147,0.9761690190917186,0.1607979714918209
       ,0.0276438810333863,0.0038405729373609,0.0003951896511919
       ,0.0000321767881768,0.0000002888167364,0.0000003960315187)
  
  y<-idum-0.5
  if(abs(y)<0.42){
    r<-y*y
    x<-y*(((a3*r+a2)*r+a1)*r+a0)/((((b3*r+b2)*r+b1)*r+b0)*r+1)
  }
  else{
    r<-idum
    if(y>0){r<-1-idum}
    r<-log(-log(r))
    x<-C[1]+r*(C[2]+r*(C[3]+r*(C[4]+r*(C[5]+r*(C[6]+r*(C[7]+r*(C[8]+r*C[9])))))))
    if(y<0){x<-(-x)}
  }
  return(x)
}
#this is a function that generate normal distributed random number 
gassrand<-function(numran,idum=-1){
  if(idum>0){idum=-idum}
  randnum=rand2(numran,idum)
  gassRand=rep(0,length(randnum))
  for(i in 1:length(randnum)){
    gassRand[i]<-gassMap(randnum[i])
  }
  return(gassRand)
}
```
Function that will simulate stock price given S0,drift,vol,r
```{r}
MY_Stock_Simu<-function(num_grid,path_num,dt,drift,vol,S0){
  randomwalk<-gassrand(num_grid*path_num,0)
  randomwalk<-t(matrix(data=randomwalk,nrow = num_grid, ncol = path_num,byrow = FALSE,dimnames = NULL))
  price_path<-matrix(data = 0, nrow = path_num, ncol = num_grid+1, byrow = FALSE,dimnames = NULL)
  price_path[,1]<-rep(S0,path_num)
  #simulate stock path
  for(i in 1:path_num){
    for(j in 1:num_grid){
      price_path[i,j+1]=price_path[i,j]*exp((drift*dt+vol*sqrt(dt)*randomwalk[i,j])) 
    }
  }
  return(price_path)
}
```
# Hedging Asian Options
# option value: 10,000*Max{2*(Avg_S&P - Avg_S&P_0)/Avg_S&P_0,0}
Step 1: Simulate stock path
```{r}
#stock info 
S0<-2750
dt<-1/12
rf<-0.03
q<-0.02 #divedent yield
vol<-0.15

drift<-0.08
rf.drift<-rf-q-0.5*vol*vol


m<-60 #num of grid on each path
n<-1000 #num of path

Simu_stock<-MY_Stock_Simu(m,n,dt,drift,vol,S0)
Simu_stock_rf<-MY_Stock_Simu(m,n,dt,rf.drift,vol,S0)
```
First Simulation:
Calculating the option price and option delta under riks_neutral GBM
Function that will calculate Asian option price given n,m,stock_path
```{r}
Asian_option<-function(n,m,stock_path){
  ave_price=rep(0,n)
  option_value=rep(0,n)
  delta<-rep(0,n)
  num<-length(stock_path[1,])
  grid<-num-1
  for(i in 1:n){
    ave_price[i]=mean(stock_path[i,])
    #calculating option value
    option_value[i]=max(20000*(ave_price[i]-stock_path[i,1])/stock_path[i,1],0)*exp(-rf*dt*grid)
    if(ave_price[i]-stock_path[i,1]>0){
      delta[i]<-(exp(-rf*dt*grid)*ave_price[i]/stock_path[i,1])
    }
    else{delta[i]<-0}
  }
  option_price<-mean(option_value)
  option_delta<-mean(delta)
  return(c(option_price,option_delta))
}

#Calculating the option price and option delta under riks_neutral GBM
result<-Asian_option(n,m,Simu_stock_rf)
option.price<-result[1]
option.delta<-result[2]
cat('Under risk neutral measure\n')
cat('delta of option price is: ',option.price,'\n')
cat('option price is: ',option.delta,'\n')
```
# Second simulation:capture the evolution of the S&P 500 over the 5-year Horizon of SIIA.
```{r}
OV<-rep(0,m)#option value
OD<-rep(0,m)#option delta
for(j in m:1){
  result_temp<-Asian_option(n,m,Simu_stock[,(m-j+1):(m+1)])
  OV[m+1-j]<-result_temp[1]
  OD[m+1-j]<-result_temp[2]
}
OV
OD
length(OD)
length(OV)
```
#delta hedging 
# at each month, hedging ratio is OD, and corresponding option value is OV
# look at each path
```{r}
Hedging_cost<-OV[1]*OD[1]
for(i in 1:(m-1)){
  if(OD[i]<=OD[i+1]){#buy more option
    Hedging_cost<-Hedging_cost+OV[(i+1)]*(OD[(i+1)]-OD[i])
  }
  else{
    Hedging_cost<-Hedging_cost+OV[(i+1)]*(OD[(i+1)]-OD[i])
  }
}
cat('Hedaging cost: ',Hedging_cost,'\n')
Portflio_Value<-rep(0,n)
for(i in 1:n){
  Portflio_Value[i]<-10000+20000/Simu_stock[i,1]*max(mean(Simu_stock[i,2:(m+1)])-Simu_stock[i,1],0)
}
mean_value<-mean(Portflio_Value)-Hedging_cost
mean(Portflio_Value)
cat('Mean value of the strategy is:',mean_value,'\n')
cat('Mean return of the strategy is:',(mean_value-10000)/10000,'\n')
cat('Without hedging,the Mean return of the portfolio is: ',(mean(Portflio_Value)-10000)/10000,'\n')

```
## Question 2

Thus by hedging with the option, bank can reduce its risk.
```{r}
dt=2/52 #bi_weely grid
K=100
t=0.5
S0=100
vol=0.25
r=0.03
m<-13
n<-10000
drift<-r-0.5*vol*vol
Simu_stock<-MY_Stock_Simu(m,n,dt,drift,vol,S0)
```
(2) Evaluation for early exercise is every two weeks, I define a function to calculated American option price based on barrier that user gives
```{r }
Us_option<-function(n,m,barrier,stocke_price,K){
  option_value<-rep(0,n)
  dt<-2/52
  t_t_T<-m*dt
  r<-0.03
  t_n<-m #value every 2 weekd
  for(i in 1:n){
    for(j in 2:t_n){
     if(Simu_stock[i,j]<=barrier){
        #early exercise
        option_value[i]=(K-stocke_price[i,j])*exp(-(j)*dt*r)
        break;
      }
      option_value[i]=max((K-stocke_price[i,j]),0)*exp(-t_t_T*r)
      
    }
  }
  return( mean(option_value))
}

```
(3) Determine the level of the barrier that maximized the value of the put option
To make my code more effient:
First,I use a series a grid of 1 from K/50 to K and calculated the option price for each barrier
Second, I find the grid that has the maxinum price,best_grid1
Third, I set a a series a grid of 0.1 from (best_grid1-1) to (best_grid1+1)
Then, I find the grid that has the maxinum price,best_grid2
Then, I set a a series a grid of 0.01 from (best_grid1-1) to (best_grid1+1)
#By doing this,I can find the target grid doing the calculation for 80*n*m of precision of 0.001,  vs doing 50000*n*m  times
```{r }
barrier<-seq(50, 100, 1 )
l<-length(barrier)
option_price<-rep(0,l)
for(i in 1:l){
  option_price[i]<-Us_option(n,m,barrier[i],Simu_stock,K)
}

for(i in 1:3){
I1=which.max(option_price)
low=I1-1
up=I1+1
barrier<-seq(barrier[low], barrier[up], 1/10**i )
l<-length(barrier)
option_price<-rep(0,l)
for(j in 1:l){
  option_price[j]<-Us_option(n,m,barrier[j],Simu_stock,K)
}
}
I1=which.max(option_price)
optimized_barrier<-barrier[I1]
optimized_option_price<-option_price[I1]

cat('optimized barrier is: ',optimized_barrier)
cat('\noptimized American option price is',optimized_option_price)
cat('\nEuropean option price is: ',Us_option(n,m,0,Simu_stock,K))#given a barrier that stock price cannot reach==>Np early exercise==>european option price
```

As we can see that our American option price > European option price for the same parameters,which is consistent with the reality that American option is expensive than European option.

## Check the value of the American put against the value determined by a Binomial Model
```{r }
# Binomial Model
numsteps<-13
DelT <- 2/52 
uptick<-exp(+vol*sqrt(DelT))
dntick<-exp(-vol*sqrt(DelT))
FVFactor<-exp(r*DelT)
probup<-(FVFactor-dntick)/(uptick-dntick)
probdn<-1-probup
SMat<-matrix(rep(0),nrow=numsteps,ncol=numsteps)
EMat<-matrix(rep(0),nrow=numsteps,ncol=numsteps)
AMat<-matrix(rep(0),nrow=numsteps,ncol=numsteps)
for (i in 1:numsteps) {
  for (j in 1:i) {
    SMat[j,i]<-S0*uptick^(i-j)*dntick^(j-1) 
}}

i<-numsteps
for (j in 1:i) {
  EMat[j,numsteps]<-max(K-SMat[j,numsteps],0)
  AMat[j,numsteps]<-max(K-SMat[j,numsteps],0)
}
i<-i-1
while (i > 0) {
  for (j in 1:i) {
    EMat[j,i] <- (1/FVFactor)*(probup*EMat[j,i+1] + probdn*EMat[j+1,i+1])
    AMat[j,i] <- (1/FVFactor)*(probup*AMat[j,i+1] + probdn*AMat[j+1,i+1])
    AMat[j,i] <- max(AMat[j,i],K-SMat[j,i])
    }
    i<-i-1
}

cat('European option price is: ',EMat[1,1],'\n')
cat('American option price is: ',AMat[1,1],'\n')
```

## Question 3
```{r}
numreg <-100
var5 <-rep(0,numreg)
var25 <- rep(0,numreg)
vavg <- rep(0,numreg)
cavg <- rep(0,numreg)
lcount <-1

numran<-1000000
rand_norm_c <- gassrand(numran)


  
  Dnum <-100
  rand_uniform_c <-rand2(Dnum)
  
  portfolio<-rep(0,Dnum)
  portfolio2<-rep(0,Dnum)
  ran100 <-as.integer(rand_uniform_c*100)+1
  for(icount in 1:Dnum){
    portfolio[icount]<-ran100[icount]*10000
  }

  AMatrix <-matrix(rnorm(Dnum^2),Dnum, Dnum)
  CovarM  <- (crossprod(AMatrix))/100
  AMatrix <-chol(CovarM)
  AMatrixt <- t(AMatrix)
  DeltaT <-1/254
  Volatility<-diag(CovarM)
  randZ <- rep(0,Dnum)
  numruns <-100
  P0 <-sum(portfolio)
  rets<-rep(0,numruns)
  TotalLoss <- rep(0,numruns)
  PercentLoss<-rep(0,numruns)
  dollar_rets<-rep(0,numruns)
  for(icount in 1:Dnum){
    default<-rep(0,Dnum)
    loss<-rep(0,Dnum)
    for(jcount in 1:Dnum){
      randZ[jcount]<-rand_norm_c[lcount]
      lcount<-lcount+1
    }
    ZVals<-AMatrixt%*%randZ
    for(jcount in 1:Dnum){
      if(-Volatility[jcount]>ZVals[jcount]){
        #Volatility[jcount]
        
        default[jcount]<-1
        loss[jcount]<-portfolio[jcount]*0.2
      }
      portfolio2[jcount]<-portfolio[jcount]*exp(((-0.5*Volatility[jcount]^2)*DeltaT)-sqrt(DeltaT)*ZVals[jcount])
    }
    P1<-sum(portfolio2)
    TotalLoss[icount]<-sum(loss)
    PercentLoss[icount]<-TotalLoss[icount]/P0
    rets[icount]<-log(P1/P0)
    dollar_rets[icount]<-P1-P0
  }

```

```{r}
cat('the level of loss of the portfolio',TotalLoss,'\n')
a=sort(PercentLoss)
n=as.integer(length(a)*0.05)
cat('percentage loss of losses at the 5% probability level is ',a[n])
```