---
title: "Simu HW#3 Q3"
author: "Yu DAI"
date: "2019/4/28"
output: html_document
---
### Assumption for Q3:
Bond info:
(1) Time to maturity: 5 year
(2) coupon rate: 6% (annually)
Interest rate is continously compounded
Volatility for interest rate is: 0.05

```{r }
rand2<-function(numran,idum=-1){  
  IM1=2147483563
  IM2=2147483399
  IMM1=IM1-1
  IA1=40014
  IA2=40692
  IQ1=53668
  IQ2=52774
  IR1=12211
  IR2=3791
  NTAB=32
  NDIV=1+IMM1/NTAB
  #make sure that you initializa the generator with a non-positive idum. 
  if(idum>0){idum=-idum}
  
  idum2=123456789
  iv=rep(0,NTAB)
  iy=0
  #real number
  AM=1./IM1
  EPS=1.2e-7
  RNMX=1.-EPS#number very close to 1
  random<-rep(0,numran)
  icount=1
  for(icount in 1:numran){
    if(idum<=0){
      idum<-max(-idum,1)
      idum2=idum
      j=NTAB+8
      while(j>0){
        k<-as.integer(idum/IQ1)
        idum<-IA1*(idum-k*IQ1)-k*IR1
        if(idum<0){
          idum<-idum+IM1
        }
        if(j<33){iv[j]<-idum}
        j<-j-1
      }
      iy<-iv[1]
    }
    k<-as.integer(idum/IQ1)
    idum<-IA1*(idum-k*IQ1)-k*IR1
    if(idum<0){idum<-idum+IM1}
    k<-as.integer(idum2/IQ2)
    idum2=IA2*(idum2-k*IQ2)-k*IR2
    if(idum2<0){idum2<-idum2+IM2}
    j<-1+as.integer(iy/NDIV)
    iy<-iv[j]-idum2
    iv[j]<-idum
    if(iy<1){iy<-iy+IMM1}
    ran2<-min(AM*iy,RNMX)
    random[icount]<-ran2
  }
  return(random)
}
```

```{r }
gassMap<-function(idum){
  #input: idum between 0 and 1
  #output: x,approximation to inverse normal cdf
  a0=2.50662823884
  a1=-18.61500062529
  a2=41.39119773534
  a3=-25.44106049637
  b0=-8.47351093090
  b1=23.08336743743
  b2=-21.06224101826
  b3=3.13082909833
  C<-c(0.3374754822726147,0.9761690190917186,0.1607979714918209
       ,0.0276438810333863,0.0038405729373609,0.0003951896511919
       ,0.0000321767881768,0.0000002888167364,0.0000003960315187)
  
  y<-idum-0.5
  if(abs(y)<0.42){
    r<-y*y
    x<-y*(((a3*r+a2)*r+a1)*r+a0)/((((b3*r+b2)*r+b1)*r+b0)*r+1)
  }
  else{
    r<-idum
    if(y>0){r<-1-idum}
    r<-log(-log(r))
    x<-C[1]+r*(C[2]+r*(C[3]+r*(C[4]+r*(C[5]+r*(C[6]+r*(C[7]+r*(C[8]+r*C[9])))))))
    if(y<0){x<-(-x)}
  }
  return(x)
}
#this is a function that generate normal distributed random number 
gassrand<-function(numran,idum=-1){
  if(idum>0){idum=-idum}
  randnum=rand2(numran,idum)
  gassRand=rep(0,length(randnum))
  for(i in 1:length(randnum)){
    gassRand[i]<-gassMap(randnum[i])
  }
  return(gassRand)
}
hist(gassrand(10000))

```
### Bond Option Pricing Under Ho_lee's Framework
## Step1: generate forward rate F(0:t1,t2) in continoua compounded situation
# P_t_T: Present Value of 1 dollar at maturity t=0,1,2,3,4,5
```{r }
#observed spot rate is:
spot<-c(0.01,0.02,0.025,0.03,0.0325)
#corresponding time of observed spot rate is:
time<-c(1,2,3,4,5)
# the Worth of 1 dollar @ 0,1,2,3,4,5 year at today 
P_t_T<-rep(0,5)
for(i in 1:5){
  P_t_T[i]=1*exp(-spot[i]*i)
}
cat('Present Value of 1 dollar at maturity t=1,2,3,4,5\n')
P_t_T
#forward rate F(0:t1,t2) is:
forward_rate=rep(0,5)
forward_rate[1]=spot[1]
for(i in 2:5){
  forward_rate[i]=log(P_t_T[i-1]/P_t_T[i])/1
}
cat('Implied forward rate oberserved today:\n')
for(i in 1:5){
  cat('time',i-1,'~time',i,' : ',forward_rate[i],'\n')
}
```
## Step2: Estimated bond price of today
```{r }
#Bond info:
FV=100    #face value
C=0.06*FV #coupon payment
PV_C1=C*exp(-spot[1])
PV_C2=C*exp(-spot[1]-forward_rate[2])
PV_C3=C*exp(-spot[1]-forward_rate[2]-forward_rate[3])
PV_C4=C*exp(-spot[1]-forward_rate[2]-forward_rate[3]-forward_rate[4])
PV_C5=C*exp(-spot[1]-forward_rate[2]-forward_rate[3]-forward_rate[4]-forward_rate[5])
PV_FV=FV*exp(-spot[1]-forward_rate[2]-forward_rate[3]-forward_rate[4]-forward_rate[5])
PV_Bond=PV_C1+PV_C2+PV_C3+PV_C4+PV_C5+PV_FV
PV_Bond
```
## Step 3: Simulate interest rate under Ho_Lee Model,path=10000, each path with 4 grid
```{r }
Ho_Lee_interest<-function(num_grid,path_num,vol,r0,forward){
  #generate random number
  randomwalk<-gassrand(num_grid*path_num,0)
  
  randomwalk<-t(matrix(data=randomwalk,nrow = num_grid, ncol = path_num,byrow = FALSE,dimnames = NULL))
  
  interest_path<-matrix(data = 0, nrow = path_num, ncol = num_grid+1, byrow = FALSE,dimnames = NULL)
  
  delta_T=1
  #simulate stock path
  interest_path[,1]<-rep(r0, path_num)
  for(i in 1:path_num){
    for(j in 1:num_grid){
      interest_path[i,j+1]=interest_path[i,j]+(forward[j+1]-forward[j])+0.5*vol*vol*((j)^2-(j-1)^2)+vol*sqrt(delta_T)*randomwalk[i,j]
    }
  }
  return(interest_path)
}

sigma <- 0.05
num_grid<-4
path_num<-10000
Ho_Lee_of_interest<-Ho_Lee_interest(num_grid,path_num,sigma,spot[1],forward_rate)
cat('Implied forward rate oberserved today:\n')
for(i in 1:4){
  cat('time',i,'~time',i+1,' : ',forward_rate[i],'\n')
}
cat('Expeacted Value of  1 year rate at year 1:',mean(Ho_Lee_of_interest[,2]),'\n')
cat('Expeacted Value of  2 year rate at year 1:',mean(Ho_Lee_of_interest[,3]),'\n')
cat('Expeacted Value of  3 year rate at year 1:',mean(Ho_Lee_of_interest[,4]),'\n')
cat('Expeacted Value of  4 year rate at year 1:',mean(Ho_Lee_of_interest[,5]),'\n')

hist(Ho_Lee_of_interest[,2],main='Distribution of 1 year rate at year 1')
hist(Ho_Lee_of_interest[,3],main='Distribution of 2 year rate at year 1')
hist(Ho_Lee_of_interest[,4],main='Distribution of 3 year rate at year 1')
hist(Ho_Lee_of_interest[,5],main='Distribution of 4 year rate at year 1')
###
```
### Step 4: Calculated Bond price at year 1 and computing option price
```{r }
K=100 #strike price
bond_price<-rep(0,path_num)
call_option_value<-rep(0,path_num)
for(i in 1:path_num){
  for(j in 2:num_grid)
    bond_price[i]= bond_price[i]+C*exp(-Ho_Lee_of_interest[i,j])
    if(j==num_grid){
      bond_price[i]=bond_price[i]+FV*exp(-Ho_Lee_of_interest[i,j])
    }
  call_option_value[i]<-max(bond_price[i]-K,0)
}
Call_price<-mean(call_option_value)
cat("Call option price for bond is:",Call_price)
```
### Bond Option Pricing Under Vasicek's Framework
## Step1 : Simulate interest rate under Vasicek Model,path=10000, each path with 4 grid
```{r }
Vasicek_interest<-function(num_grid,path_num,r0,forward,alpha,vol){
  #generate random number
  randomwalk<-gassrand(num_grid*path_num,0)
  
  randomwalk<-t(matrix(data=randomwalk,nrow = num_grid, ncol = path_num,byrow = FALSE,dimnames = NULL))
  
  interest_path<-matrix(data = 0, nrow = path_num, ncol = num_grid+1, byrow = FALSE,dimnames = NULL)
  dt=1
  #simulate stock path
  interest_path[,1]<-rep(0, path_num)
  for(i in 1:path_num){
    for(j in 1:num_grid){
      interest_path[i,j+1]=interest_path[i,j]*exp(-alpha*dt)+(forward[j+1]-forward[j])+vol*vol*(1-exp(-2*alpha*dt))/(2*alpha)*sqrt(dt)*randomwalk[i,j]
    }
  }
  return(interest_path)
}
alpha=0.1
sigma=0.015
num_grid=4
path_num=10000
Vasicek_interest_rate<-Vasicek_interest(num_grid,path_num,spot[1],forward_rate,alpha,sigma)
cat('Implied forward rate oberserved today:\n')
for(i in 1:4){
  cat('time',i,'~time',i+1,' : ',forward_rate[i],'\n')
}
cat('Expeacted Value of  1 year rate at year 1:',mean(Vasicek_interest_rate[,2]),'\n')
cat('Expeacted Value of  2 year rate at year 1:',mean(Vasicek_interest_rate[,3]),'\n')
cat('Expeacted Value of  3 year rate at year 1:',mean(Vasicek_interest_rate[,4]),'\n')
cat('Expeacted Value of  4 year rate at year 1:',mean(Vasicek_interest_rate[,5]),'\n')

hist(Vasicek_interest_rate[,2],main='Distribution of 1 year rate at year 1')
hist(Vasicek_interest_rate[,3],main='Distribution of 2 year rate at year 1')
hist(Vasicek_interest_rate[,4],main='Distribution of 3 year rate at year 1')
hist(Vasicek_interest_rate[,5],main='Distribution of 4 year rate at year 1')
###
```
## Step2: Estimated bond price of today
```{r }
K=100 #strike price
bond_price<-rep(0,path_num)
call_option_value<-rep(0,path_num)
for(i in 1:path_num){
  for(j in 2:num_grid)
    bond_price[i]= bond_price[i]+C*exp(-Vasicek_interest_rate[i,j])
    if(j==num_grid){
      bond_price[i]=bond_price[i]+FV*exp(-Vasicek_interest_rate[i,j])
    }
  call_option_value[i]<-max(bond_price[i]-K,0)
}
Call_price<-mean(call_option_value)
cat("Call option price for bond is:",Call_price)
```