---
title: "Simulation HW2"
author: "Yu DAI"
date: "2019/4/6"
output: html_document
---

```{r, echo=FALSE}
rand2<-function(numran,idum=-1){  
  IM1=2147483563
  IM2=2147483399
  IMM1=IM1-1
  IA1=40014
  IA2=40692
  IQ1=53668
  IQ2=52774
  IR1=12211
  IR2=3791
  NTAB=32
  NDIV=1+IMM1/NTAB
  #make sure that you initializa the generator with a non-positive idum. 
  if(idum>0){idum=-idum}
  
  idum2=123456789
  iv=rep(0,NTAB)
  iy=0
  #real number
  AM=1./IM1
  EPS=1.2e-7
  RNMX=1.-EPS#number very close to 1
  random<-rep(0,numran)
  icount=1
  for(icount in 1:numran){
    if(idum<=0){
    idum<-max(-idum,1)
    idum2=idum
    j=NTAB+8
   while(j>0){
        k<-as.integer(idum/IQ1)
        idum<-IA1*(idum-k*IQ1)-k*IR1
        if(idum<0){
          idum<-idum+IM1
        }
        if(j<33){iv[j]<-idum}
        j<-j-1
    }
    iy<-iv[1]
    }
    k<-as.integer(idum/IQ1)
    idum<-IA1*(idum-k*IQ1)-k*IR1
    if(idum<0){idum<-idum+IM1}
    k<-as.integer(idum2/IQ2)
    idum2=IA2*(idum2-k*IQ2)-k*IR2
    if(idum2<0){idum2<-idum2+IM2}
    j<-1+as.integer(iy/NDIV)
    iy<-iv[j]-idum2
    iv[j]<-idum
    if(iy<1){iy<-iy+IMM1}
    ran2<-min(AM*iy,RNMX)
    random[icount]<-ran2
  }
  return(random)
}
hist(rand2(1000*12,0))
hist(rand2(10000*12,0))
```

```{r }
##this is a function that mapping uniform random number into normal distribution random number
gassMap<-function(idum){
  #input: idum between 0 and 1
  #output: x,approximation to inverse normal cdf
  a0=2.50662823884
  a1=-18.61500062529
  a2=41.39119773534
  a3=-25.44106049637
  b0=-8.47351093090
  b1=23.08336743743
  b2=-21.06224101826
  b3=3.13082909833
  C<-c(0.3374754822726147,0.9761690190917186,0.1607979714918209
       ,0.0276438810333863,0.0038405729373609,0.0003951896511919
       ,0.0000321767881768,0.0000002888167364,0.0000003960315187)
  
  y<-idum-0.5
  if(abs(y)<0.42){
    r<-y*y
    x<-y*(((a3*r+a2)*r+a1)*r+a0)/((((b3*r+b2)*r+b1)*r+b0)*r+1)
  }
  else{
    r<-idum
    if(y>0){r<-1-idum}
    r<-log(-log(r))
    x<-C[1]+r*(C[2]+r*(C[3]+r*(C[4]+r*(C[5]+r*(C[6]+r*(C[7]+r*(C[8]+r*C[9])))))))
    if(y<0){x<-(-x)}
  }
  return(x)
}
#this is a function that generate normal distributed random number 
gassrand<-function(numran,idum=-1){
  if(idum>0){idum=-idum}
  randnum=rand2(numran,idum)
  gassRand=rep(0,length(randnum))
  for(i in 1:length(randnum)){
    gassRand[i]<-gassMap(randnum[i])
  }
  return(gassRand)
}

hist(gassrand(1000*12,0))
hist(gassrand(10000*12,0))
```

```{r , echo=FALSE}
#Geometric Brownian motion:
#St+1/St=exp((r- 0.5*sigma*sigma)*dt+sigma*sqrt(dt)*error)
#This is a function that calculate price simulation result 
option_price1<-function(T=1,num_grid=12,r=0,sigma=0,path_num=1,S0=100,
                        K=100,CallorPut='C'){
  #time grid
  dt<-T/num_grid
  randomwalk<-gassrand(num_grid*path_num,0)
  randomwalk<-t(matrix(data=randomwalk,nrow = num_grid,
                       ncol = path_num,byrow = FALSE,dimnames = NULL))
  price_path<-matrix(data = 0, nrow = path_num, 
                     ncol = num_grid+1, byrow = FALSE,dimnames = NULL)
  price_path[,1]<-rep(S0,path_num)#give initial value to each path
  #simulate stock path
  for(i in 1:path_num){
    for(j in 1:num_grid){
      price_path[i,j+1]=price_path[i,j]*exp((r-0.5*sigma**2)*dt +sigma*sqrt(dt)*randomwalk[i,j])
    }
  }
  #calulating 95% confidence interval for stock at each grid:
  lw<-exp(log(S0)+(r-0.5*sigma**2)*T-1.96*sigma*sqrt(T))#lower bound
  up<-exp(log(S0)+(r-0.5*sigma**2)*T+1.96*sigma*sqrt(T))#higher bound

  #option pricing 
  path_price<-rep(0,path_num)
  if(CallorPut=='C'){
    for(i in 1:path_num){
      path_price[i]=max(max(price_path[i,2:(num_grid+1)])-K,0)
    }
    hist(path_price,main = paste("Histogram of" , 'Call Option value'))
  }
  else{
    for(i in 1:path_num){
      path_price[i]=max(price_path[i,(num_grid+1)]-min(price_path[i,2:(num_grid+1)]),0)
    }
    hist(path_price,main = paste("Histogram of" , 'Put Option value'))
  }
  option_lw<-(mean(path_price)-1.96*sd(path_price)/sqrt(length(path_price)))*exp(-r*T)
  option_up<-mean(path_price)+1.96*sd(path_price)/sqrt(length(path_price))*exp(-r*T)
  cat("95% Confidence interval is:" ,"[",option_lw,",",option_up,']','\n')
  return(path_price)
}
```
##Stock information as follows:
```{r ,echo=FALSE}
T<-1#Time to maturity
num_grid<-12
r<-0.03#interest rate
sigma<-0.25#volatility of stock price
path_num1=1000#simulation path
path_num2=10000#simualtion path
S0<-100
K<-100

#call option:1000 path
call_price1<-option_price1(T,num_grid,r,sigma,path_num1,S0,K,'C')
Call_price1<-mean(call_price1)*exp(-r*T)
Call_price1
```

```{r,echo=FALSE}
#call option:10000 path
call_price2<-option_price1(T,num_grid,r,sigma,path_num2,S0,K,'C')
Call_price2<-mean(call_price2)*exp(-r*T)
Call_price2
```
```{r,echo=FALSE}
#floating option:1000 path
put_price1<-option_price1(T,num_grid,r,sigma,path_num1,S0,K,'P')
Put_price1<-mean(put_price1)*exp(-r*T)
Put_price1
```
```{r,echo=FALSE}
#floating option:10000 path
put_price2<-option_price1(T,num_grid,r,sigma,path_num2,S0,K,'P')
Put_price2<-mean(put_price2)*exp(-r*T)
Put_price2
```
## Given a positive definite symmetrix matrix a[n,n],with physical dimension np, this routine construct its Cholesky decomposition, A=L*L^T. The function return the diagonal elements of Cholesky factor L 
```{r,echo=FALSE}
choldc<-function(a,n){
  #a: n by n positive-definite symmetric matrix
  #p: vector
  sum<-0
  p<-rep(0,n)
  for(i in 1:n){
    for(j in i:n){
      sum<-a[i,j]
      k=i-1
      while(k>=1){
        sum=sum-a[i,k]*a[j,k]
        k=k-1
      }
      if(i==j){
        if(sum<=0){
          cat("choldc failed")
          
        }
        p[i]=sqrt(sum)
        }
      else{
        a[j,i]=sum/p[i]
      }
    }
  }
  a
  return(p)
}

#alternative method
#a.chol<-chol(test)
#a.chol
``` 
---
This is a part that will implement Quantos
Data Source:
(1) Stock infomation(AAPL) on 2019/04/04
S1(0)=194.961805(dividend adjusted spot price)
sigma0=0.054883 (annulized volatility)
USD.r=0.0244 (interest rate: using three month treasury rate)
EUROS.r=-0.0035886

(2) Euros/USD exchange rate
S2(0)=0.891200
sigma1=0.054184(annulized volatility)
mean=0.000298 

(3) At the money option:
AAPL Jul 2019 195 call
Maturity=07/19/2019
option price=10.9

(3) At the money option:
t=0.25 time to maturity (3 month)
K=S1(0)*S2(0)=173.75
dt=t/63(Because there are 63 trade days in 3 month)
---
##Simulation process
```{r,echo=FALSE}
#stock info 
stock.S0=194.961805#adjusted future dividend
# Euros/USD exchange rate
exchange.S0=0.8912
exchange.mean=0.00036832
#interest rate and time to maturity
K=stock.S0*exchange.S0
USD.r=0.0244 
EUROS.r=-0.0035886  


```
```{r,echo=FALSE}
library(readxl)
data <- read_excel("/Users/daiyu/Desktop/AAPL&exchange 2.xlsx",col_names = FALSE, col_types = c("text", "numeric", "numeric", "numeric", "numeric","text","text"))
stock.dailyret<-(data$..3[1:61])
stock.dailyret
exchange.dailyret<-(data$..5[1:61])
exchange.dailyret
stock.ret0<-stock.dailyret[1]
exchange.ret0<-exchange.dailyret[1]
```
## Calculate variance matrix between daily changes in stock return and exchange rate changes
```{r,echo=FALSE}
stock_exchange<-cbind(stock.dailyret,exchange.dailyret)
stock_exchange.var<-var(stock_exchange)
stock_exchange.var
stock_exchange.cor<-cor(stock_exchange)
stock_exchange.cor

```
## cholesky decomposing of variance matrix of stock and exchange rate
```{r,echo=FALSE}
vector.A<-choldc(stock_exchange.var,2)
chol(stock_exchange.var)
vector.A
stock.sigma<-vector.A[1]*sqrt(251)#stock has 252 trade days,so 251 data return each year 
stock.sigma
exchange.sigma<-vector.A[2]*sqrt(336)#echange rate has 337 trade days,so 336 data return each year 
exchange.sigma
```
## Simulating Process

```{r,echo=FALSE}
#step 1: generate 2 random variable X1,X2
path1<-1000
grid<-63
t<-0.25
dt<-t/grid
X1<-gassrand(1000*63,0)#seed:0
X2<-gassrand(1000*63,-1)#seed:-1

randomwalk1.error1<-X1
randomwalk1.error2<-stock_exchange.cor[1,2]*X1+sqrt(1-stock_exchange.cor[1,2]**2)*X2
randomwalk1.error1<-t(matrix(data=randomwalk1.error1,nrow = grid, ncol = path1,byrow = FALSE,dimnames = NULL))
randomwalk1.error2<-t(matrix(data=randomwalk1.error2,nrow = grid, ncol = path1,byrow = FALSE,dimnames = NULL))
#step 2: Simulate 3-month returns for the Stock and Euro/USD exchange rate 
#path=1000
Simu.stockret<-matrix(data=NA,nrow =path1,ncol = grid+1 )
Simu.stockprice<-matrix(data=NA,nrow =path1,ncol = grid+1 )
Simu.exchangeret<-matrix(data=NA,nrow =path1,ncol = grid+1 )
Simu.exchangeprice<-matrix(data=NA,nrow =path1,ncol = grid+1 )
for(i in 1:path1){
  Simu.stockprice[i,1]<-stock.S0
  Simu.stockret[i,1]<-stock.ret0
  Simu.exchangeret[i,1]<-exchange.ret0
  Simu.exchangeprice[i,1]<-exchange.S0
  
  for(j in 2:(grid+1)){
    Simu.stockret[i,j]<-Simu.stockret[i,j-1]+(USD.r-0.5*stock.sigma**2)*dt+stock.sigma*sqrt(dt)*randomwalk1.error1[i,j-1]
    Simu.exchangeret[i,j]<-Simu.exchangeret[i,j-1]+(EUROS.r-USD.r-0.5*exchange.sigma**2)*dt+exchange.sigma*sqrt(dt)*randomwalk1.error2[i,j-1]
    Simu.stockprice[i,j]<-Simu.stockprice[i,j-1]*exp((USD.r-0.5*stock.sigma**2)*dt+stock.sigma*sqrt(dt)*randomwalk1.error1[i,j-1])
    Simu.exchangeprice[i,j]<-Simu.exchangeprice[i,j-1]*exp((EUROS.r-USD.r-0.5*exchange.sigma**2)*dt+exchange.sigma*sqrt(dt)*randomwalk1.error2[i,j-1])
  }
}
## Option Pricing 

M_price<- Simu.stockprice[,grid+1]*Simu.exchangeprice[,grid+1]
hist(M_price,main = "Stock Price at maturity in Euros")
compare<-function(a){
  if(a>0){return(a)}
  else{return(0)}
}

option_value<-as.matrix(M_price-K)
option_value<-apply(option_value,1,compare)
hist(option_value,main="Option values at maturity in Euros")
Call_option_price<-mean(option_value)*exp(-EUROS.r*t)
Call_option_price
option_lw<-(mean(option_value)-1.96*stdev(option_value)/sqrt(length(option_value)))*exp(-EUROS.r*t)
option_up<-mean(option_value)+1.96*stdev(option_value)/sqrt(length(option_value))*exp(-EUROS.r*t)
cat("95% Confidence interval is:" ,"[",option_lw,",",option_up,']','\n')
### problen with confidence interval calculation 
```
# 95% confidence bounds for simulations with 1,000  estimates.
```{r,echo=FALSE}
#95% confidence bounds for simulations with 1,000  estimates.
#lower bound
stock.lw<-exp(log(stock.S0)+(USD.r-0.5*stock.sigma**2)*t-1.96*stock.sigma*sqrt(t))
exchange.lw<-exp(log(exchange.S0)+(exchange.mean-0.5*exchange.sigma**2)*t-1.96*exchange.sigma*sqrt(t))
option.lw<-stock.lw*exchange.lw-K
#higher bound
stock.up<-exp(log(stock.S0)+(USD.r-0.5*stock.sigma**2)*t+1.96*stock.sigma*sqrt(t))
exchange.up<-exp(log(exchange.S0)+(exchange.mean-0.5*exchange.sigma**2)*t+1.96*exchange.sigma*sqrt(t))
option.up<-stock.up*exchange.up-K

option_value_df<-data.frame(option_value)
option_value_ci<-subset(option_value_df,option_value>=option.lw & option_value<=option.up)
hist(option_value_ci$option_value,main="Option Value with 95% Confidence")
option_lw<-(mean(option_value)-1.96*stdev(option_value)/sqrt(length(option_value)))*exp(-r*T)
option_up<-mean(option_value)+1.96*stdev(option_value)/sqrt(length(option_value))*exp(-r*T)
cat("confidence inter is: [",max(option.lw,0),',',option.up,']')

```
## Path=10000
```{r,echo=FALSE}
path1<-10000
grid<-63
t<-0.25
dt<-t/grid
X1<-gassrand(10000*63,0)#seed:0
X2<-gassrand(10000*63,-1)#seed:-1

randomwalk1.error1<-X1
randomwalk1.error2<-stock_exchange.cor[1,2]*X1+sqrt(1-stock_exchange.cor[1,2]**2)*X2
randomwalk1.error1<-t(matrix(data=randomwalk1.error1,nrow = grid, ncol = path1,byrow = FALSE,dimnames = NULL))
randomwalk1.error2<-t(matrix(data=randomwalk1.error2,nrow = grid, ncol = path1,byrow = FALSE,dimnames = NULL))

#step 2: Simulate 3-month returns for the Stock and Euro/USD exchange rate 
#path=10000

Simu.stockret<-matrix(data=NA,nrow =path1,ncol = grid+1 )
Simu.stockprice<-matrix(data=NA,nrow =path1,ncol = grid+1 )
Simu.exchangeret<-matrix(data=NA,nrow =path1,ncol = grid+1 )
Simu.exchangeprice<-matrix(data=NA,nrow =path1,ncol = grid+1 )
for(i in 1:path1){
  Simu.stockprice[i,1]<-stock.S0
  Simu.stockret[i,1]<-stock.ret0
  Simu.exchangeret[i,1]<-exchange.ret0
  Simu.exchangeprice[i,1]<-exchange.S0
  
  for(j in 2:(grid+1)){
    Simu.stockret[i,j]<-Simu.stockret[i,j-1]+(USD.r-0.5*stock.sigma**2)*dt+stock.sigma*sqrt(dt)*randomwalk1.error1[i,j-1]
    Simu.exchangeret[i,j]<-Simu.exchangeret[i,j-1]+(exchange.mean-0.5*exchange.sigma**2)*dt+exchange.sigma*sqrt(dt)*randomwalk1.error2[i,j-1]
    Simu.stockprice[i,j]<-Simu.stockprice[i,j-1]*exp((USD.r-0.5*stock.sigma**2)*dt+stock.sigma*sqrt(dt)*randomwalk1.error1[i,j-1])
    Simu.exchangeprice[i,j]<-Simu.exchangeprice[i,j-1]*exp((exchange.mean-0.5*exchange.sigma**2)*dt+exchange.sigma*sqrt(dt)*randomwalk1.error2[i,j-1])
  }
}

## Option Pricing 

M_price<- Simu.stockprice[,grid+1]*Simu.exchangeprice[,grid+1]
hist(M_price,main = "Stock Price at maturity in Euros")
compare<-function(a){
  if(a>0){return(a)}
  else{return(0)}
}
option_value<-as.matrix(M_price-K)
option_value<-apply(option_value,1,compare)
hist(option_value,main="Option values at maturity in Euros,path=10,000")
Call_option_price<-mean(option_value)*exp(-EUROS.r*t)
Call_option_price
option_lw<-(mean(option_value)-1.96*stdev(option_value)/sqrt(length(option_value)))*exp(-EUROS.r*t)
option_up<-mean(option_value)+1.96*stdev(option_value)/sqrt(length(option_value))*exp(-EUROS.r*t)
cat("95% Confidence interval is:" ,"[",option_lw,",",option_up,']','\n')
```
# 95% confidence bounds for simulations with 1,0000  estimates.
```{r,echo=FALSE}
#95% confidence bounds for simulations with 1,0000  estimates.
#lower bound
stock.lw<-exp(log(stock.S0)+(USD.r-0.5*stock.sigma**2)*t-1.96*stock.sigma*sqrt(t))
exchange.lw<-exp(log(exchange.S0)+(exchange.mean-0.5*exchange.sigma**2)*t-1.96*exchange.sigma*sqrt(t))
option.lw<-stock.lw*exchange.lw-K
#higher bound
stock.up<-exp(log(stock.S0)+(USD.r-0.5*stock.sigma**2)*t+1.96*stock.sigma*sqrt(t))
exchange.up<-exp(log(exchange.S0)+(exchange.mean-0.5*exchange.sigma**2)*t+1.96*exchange.sigma*sqrt(t))
option.up<-stock.up*exchange.up-K
hist(option_value_ci$option_value,main="Option Value with 95% Confidence")
cat("confidence inter is: [",max(option.lw,0),',',option.up,']')

```